### 2019-02-21 paper_00_fluiddyn_meta/article.tex
sed 's/section\*/section/g' article.tex
Subsection -> paragraphbf sed -i 's/subsubsection/paragraphbf/g' */article.tex
Overview etc. as sections and sub+other divisions sed -i 's/section\{/subsection\{/g' */article.tex sed -i 's/subsection[{].[[:alnum:]]. /section\{/g' */article.tex

% \section*{(1) Overview}

@@

% \section*{Title}

@@

% \section*{Paper Authors}

% \textcolor{blue}{1. Last name, first name; (Lead/corresponding author first) \\
% 2. Last name, first name; etc.}
%
% 1. AUGIER Pierre$^a$\\
% 2. MOHANAN Ashwin Vishnu$^b$\\
% 3. BONAMY Cyrille$^a$\\
%
% \smallskip
%
% $^a$ Univ. Grenoble Alpes, CNRS, Grenoble INP\footnote{Institute of Engineering
% Univ. Grenoble Alpes}, LEGI, 38000 Grenoble, France.\\
% $^b$ Linn\'e Flow Centre, Department of Mechanics, KTH, 10044 Stockholm, Sweden.
%
% \section*{Paper Author Roles and Affiliations}
% \textcolor{blue}{1. First author role and affiliation \\
% 2. Second author role and affiliation etc.}

@@

% \section*{Abstract}

@@

% \section*{Keywords}

@@

\section*{Introduction}

@@

\section{Implementation and architecture}

@@

\subsection*{Organization of the code in packages}

@@

\subsection*{API of the Python library \fluiddyn}

@@

\subsubsection*{Module \codeinline{fluiddyn.util.paramcontainer}}

@@

\subsubsection*{Module \codeinline{fluiddyn.util.serieofarrays}}

@@

\subsubsection*{Module \codeinline{fluiddyn.util.mpi}}

@@

\subsubsection*{Module \codeinline{fluiddyn.calcul.easyfft}}

@@

\subsection*{The \fluiddyn command-line utilities}

@@

% \section*{Additional system requirements}

@@

\section*{Dependencies}

@@

\item {\bf Optional:} OpenCV with Python bindings, \pack{scikit-image}.
\end{itemize}
\section*{List of contributors}

@@

% \section*{Software location:}
%
% % {\bf Archive} \textcolor{blue}{(e.g. institutional repository, general
% % repository) (required – please see instructions on journal website for
% % depositing archive copy of software in a suitable repository)}
%
% \begin{description}[noitemsep,topsep=0pt]
% \item[Name:] PyPI
% \item[Persistent identifier:] https://pypi.org/project/fluiddyn
% \item[Licence:] CeCILL-B, a BSD compatible French licence.
% \item[Publisher:] Pierre Augier
% \item[Version published:] 0.2.4
% \item[Date published:] 02/07/2018
% \end{description}
%
% {\bf Code repository}
% % \textcolor{blue}{(e.g. SourceForge, GitHub etc.) (required)}
%
% \begin{description}[noitemsep,topsep=0pt]
% \item[Name:] Bitbucket
% \item[Persistent identifier:] https://bitbucket.org/fluiddyn/fluiddyn
% \item[Licence:] CeCILL-B
% \item[Date published:] 2015
% \end{description}
%
% {\bf Emulation environment} \textcolor{blue}{(if appropriate)}

% \begin{description}[noitemsep,topsep=0pt]
% \item[Name:] \textcolor{blue}{The name of the archive.}
% \item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
% \item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
% \item[Date published:] \textcolor{blue}{dd/mm/yy}
% \end{description}

% \section*{Language}
%
% % \textcolor{blue}{Language of repository, software and supporting files.}
%
% English

\section*{(3) Reuse potential}
%
% \textcolor{blue}{Please describe in as much detail as possible the ways in
% which the software could be reused by other researchers both within and outside
% of your field. This should include the use cases for the software, and also
% details of how the software might be modified or extended (including how
% contributors should contact you) if appropriate. Also you must include details
% of what support mechanisms are in place for this software (even if there is no
% support).}
%

@@

\subsection*{Conclusions}

@@

% already included by \bibliography{../bib}
% \section*{References}

@@

\rule{\textwidth}{1pt}

{ \bf Copyright Notice} \\
Authors who publish with this journal agree to the following terms: \\

>>>>

\section{Overview}

@@

% \subsection{Title}

@@

% \subsection{Paper Authors}

% \textcolor{blue}{1. Last name, first name; (Lead/corresponding author first) \\
% 2. Last name, first name; etc.}
%
% 1. AUGIER Pierre$^a$\\
% 2. MOHANAN Ashwin Vishnu$^b$\\
% 3. BONAMY Cyrille$^a$\\
%
% \smallskip
%
% $^a$ Univ. Grenoble Alpes, CNRS, Grenoble INP\footnote{Institute of Engineering
% Univ. Grenoble Alpes}, LEGI, 38000 Grenoble, France.\\
% $^b$ Linn\'e Flow Centre, Department of Mechanics, KTH, 10044 Stockholm, Sweden.
%
% \subsection{Paper Author Roles and Affiliations}
% \textcolor{blue}{1. First author role and affiliation \\
% 2. Second author role and affiliation etc.}

@@

% \subsection{Abstract}

@@

% \subsection{Keywords}

@@

\subsection{Introduction}

@@

\subsection{Implementation and architecture}

@@

\subsubsection{Organization of the code in packages}

@@

\subsection{of the Python library \fluiddyn}

@@

\paragraphbf{Module \codeinline{fluiddyn.util.paramcontainer}}

@@

\paragraphbf{Module \codeinline{fluiddyn.util.serieofarrays}}

@@

\paragraphbf{Module \codeinline{fluiddyn.util.mpi}}

@@

\paragraphbf{Module \codeinline{fluiddyn.calcul.easyfft}}

@@

\subsection{\fluiddyn command-line utilities}

@@

% \subsection{Additional system requirements}

@@

\subsection{Dependencies}

@@

\item {\bf Optional:} OpenCV with Python bindings, \pack{scikit-image}.
\end{itemize}
\subsection{List of contributors}

@@

\subsection{Software location}

\paragraph{\bf Archive}
% \textcolor{blue}{(e.g. institutional repository, general
% repository) (required – please see instructions on journal website for
% depositing archive copy of software in a suitable repository)}

\begin{description}[noitemsep,topsep=0pt]
\item[Name:] PyPI
\item[Persistent identifier:] https://pypi.org/project/fluiddyn
\item[Licence:] CeCILL-B, a BSD compatible French licence.
\item[Publisher:] Pierre Augier
\item[Version published:] 0.2.4
\item[Date published:] 02/07/2018
\end{description}

{\bf Code repository}
% \textcolor{blue}{(e.g. SourceForge, GitHub etc.) (required)}

\begin{description}[noitemsep,topsep=0pt]
\item[Name:] Bitbucket
\item[Persistent identifier:] https://bitbucket.org/fluiddyn/fluiddyn
\item[Licence:] CeCILL-B
\item[Date published:] 2015
\end{description}

% {\bf Emulation environment} \textcolor{blue}{(if appropriate)}
%
% \begin{description}[noitemsep,topsep=0pt]
% \item[Name:] \textcolor{blue}{The name of the archive.}
% \item[Persistent identifier:] \textcolor{blue}{e.g. DOI, handle, PURL, etc.}
% \item[Licence:] \textcolor{blue}{Open license under which the software is licensed.}
% \item[Date published:] \textcolor{blue}{dd/mm/yy}
% \end{description}

\subsection{Language}

% \textcolor{blue}{Language of repository, software and supporting files.}

English

\section{Reuse potential}
%
% \textcolor{blue}{Please describe in as much detail as possible the ways in
% which the software could be reused by other researchers both within and outside
% of your field. This should include the use cases for the software, and also
% details of how the software might be modified or extended (including how
% contributors should contact you) if appropriate. Also you must include details
% of what support mechanisms are in place for this software (even if there is no
% support).}
%

@@

\subsection{Conclusions}

@@

% already included by \bibliography{../bib}
% \subsection{References}

@@

% \rule{\textwidth}{1pt}
\vspace{10pt}
\hrule
\vspace{10pt}

\paragraphbf{Copyright Notice}

Authors who publish with this journal agree to the following terms:

### 2019-02-21 paper_02_fluidsim/article.tex
Overview etc. as sections and sub+other divisions sed -i 's/section\{/subsection\{/g' */article.tex sed -i 's/subsection[{].[[:alnum:]]. /section\{/g' */article.tex

{\bf Software paper for submission to the Journal of Open Research Software} \\

\rule{\textwidth}{1pt}

\section{(1) Overview}

\vspace{0.5cm}

\section{Title}

FluidSim: modular, object-oriented Python package for high-performance CFD
simulations

\section{Paper Authors}

1. MOHANAN, Ashwin Vishnu$^a$ \\
2. BONAMY, Cyrille$^b$ \\
3. CALPE LINARES, Miguel$^b$ \\
4. AUGIER, Pierre$^b$

\smallskip

$^a$ Linn\'e Flow Centre, Department of Mechanics, KTH, 10044 Stockholm, Sweden.\\
$^b$ Univ. Grenoble Alpes, CNRS, Grenoble INP\footnote{Institute of Engineering
Univ. Grenoble Alpes}, LEGI, 38000 Grenoble, France.

\section{Paper Author Roles and Affiliations}
1. Ph.D. student, Linn\'e Flow Centre, KTH Royal Institute of Technology,
Sweden; \\
2. Research Engineer, LEGI, Universit\'e Grenoble Alpes, CNRS, France; \\
3. Ph.D. student, LEGI, Universit\'e Grenoble Alpes, CNRS, France; \\
4. Researcher, LEGI, Universit\'e Grenoble Alpes, CNRS, France

\section{Abstract}

%\textcolor{blue}{A short (ca. 100 word) summary of the software being
%described: what problem the software addresses, how it was implemented and
%architected, where it is stored, and its reuse potential.}

The Python package \fluidpack{sim} is introduced in this article as an extensible
framework for Computational Fluid Mechanics (CFD) solvers.
%
It is developed as a part of \href{https://fluiddyn.readthedocs.io}{FluidDyn}
project \citep{fluiddyn}, an effort to promote open-source and open-science
collaboration within fluid mechanics community and intended for both educational
as well as research purposes.
%
Solvers in \fluidpack{sim} are scalable, High-Performance Computing (HPC) codes
which are powered under the hood by the rich, scientific Python ecosystem and the
Application Programming Interfaces (API) provided by \fluidpack{dyn} and
\fluidpack{fft} packages \citep{fluidfft}.
%
The present article describes the design aspects of \fluidpack{sim}, which
includes use of Python as the main language; focus on the ease of use, reuse
and maintenance of the code without compromising performance.
%
The implementation details including optimization methods, modular organization
of features and object-oriented approach of using classes to implement solvers
are also briefly explained.
%
Currently, \fluidpack{sim} includes solvers for a variety of physical problems
using different numerical methods (including finite-difference methods).
%
However, this metapaper shall dwell only on the implementation and performance
of its pseudo-spectral solvers, in particular the two- and three-dimensional
Navier-Stokes solvers.
%
We investigate the performance and scalability of \fluidpack{sim} in a
state of the art HPC cluster.
%
Three similar pseudo-spectral CFD codes based on Python (Dedalus, SpectralDNS) and
Fortran (NS3D) are presented and qualitatively and quantitatively compared to
\fluidpack{sim}.
%
The source code is hosted at Bitbucket as a Mercurial repository
\href{https://bitbucket.org/fluiddyn/fluidsim}{bitbucket.org/fluiddyn/fluidsim}
and the documentation generated using Sphinx can be read online at
\href{https://fluidsim.readthedocs.io}{fluidsim.readthedocs.io}.

\section{Keywords}

% Python;\ CFD;\ HPC;\ MPI;\ modular;\ object-oriented;\ tested;\ documented;\
% open-source
0D; 1D; 2D; 3D; pseudo-spectral; finite difference; computational fluid
dynamics; sequential; MPI; GPU

\section{Introduction}

@@

\subsection{Performance}

@@

\subsection{CFD pseudo-spectral code comparisons}

@@

\section{Quality control}

@@

\section{(2) Availability}
\vspace{0.5cm}
\section{Operating system}

@@

\section{Programming language}

@@

\section{Dependencies}

@@

\section{List of contributors}

@@

\section{Software location:}

{\bf Archive}

@@

\section{Language}

@@

\section{(3) Reuse potential}

@@

\section{Acknowledgements}

@@

\section{Funding statement}

@@

\section{Competing interests}

@@

% \section{References}

@@

\rule{\textwidth}{1pt}

{\bf Copyright Notice} \\
Authors who publish with this journal agree to the following terms: \\

>>>>

% {\bf Software paper for submission to the Journal of Open Research Software} \\
%
% \rule{\textwidth}{1pt}

\section{Overview}
%
% \vspace{0.5cm}
%
% \subsection{Title}
%
% FluidSim: modular, object-oriented Python package for high-performance CFD
% simulations
%
% \subsection{Paper Authors}
%
% 1. MOHANAN, Ashwin Vishnu$^a$ \\
% 2. BONAMY, Cyrille$^b$ \\
% 3. CALPE LINARES, Miguel$^b$ \\
% 4. AUGIER, Pierre$^b$
%
% \smallskip
%
% $^a$ Linn\'e Flow Centre, Department of Mechanics, KTH, 10044 Stockholm, Sweden.\\
% $^b$ Univ. Grenoble Alpes, CNRS, Grenoble INP\footnote{Institute of Engineering
% Univ. Grenoble Alpes}, LEGI, 38000 Grenoble, France.
%
% \subsection{Paper Author Roles and Affiliations}
% 1. Ph.D. student, Linn\'e Flow Centre, KTH Royal Institute of Technology,
% Sweden; \\
% 2. Research Engineer, LEGI, Universit\'e Grenoble Alpes, CNRS, France; \\
% 3. Ph.D. student, LEGI, Universit\'e Grenoble Alpes, CNRS, France; \\
% 4. Researcher, LEGI, Universit\'e Grenoble Alpes, CNRS, France
%
% \subsection{Abstract}
%
%\textcolor{blue}{A short (ca. 100 word) summary of the software being
%described: what problem the software addresses, how it was implemented and
%architected, where it is stored, and its reuse potential.}

% The Python package \fluidpack{sim} is introduced in this article as an extensible
% framework for Computational Fluid Mechanics (CFD) solvers.
% %
% It is developed as a part of \href{https://fluiddyn.readthedocs.io}{FluidDyn}
% project \citep{fluiddyn}, an effort to promote open-source and open-science
% collaboration within fluid mechanics community and intended for both educational
% as well as research purposes.
% %
% Solvers in \fluidpack{sim} are scalable, High-Performance Computing (HPC) codes
% which are powered under the hood by the rich, scientific Python ecosystem and the
% Application Programming Interfaces (API) provided by \fluidpack{dyn} and
% \fluidpack{fft} packages \citep{fluidfft}.
% %
% The present article describes the design aspects of \fluidpack{sim}, which
% includes use of Python as the main language; focus on the ease of use, reuse
% and maintenance of the code without compromising performance.
% %
% The implementation details including optimization methods, modular organization
% of features and object-oriented approach of using classes to implement solvers
% are also briefly explained.
% %
% Currently, \fluidpack{sim} includes solvers for a variety of physical problems
% using different numerical methods (including finite-difference methods).
% %
% However, this metapaper shall dwell only on the implementation and performance
% of its pseudo-spectral solvers, in particular the two- and three-dimensional
% Navier-Stokes solvers.
% %
% We investigate the performance and scalability of \fluidpack{sim} in a
% state of the art HPC cluster.
% %
% Three similar pseudo-spectral CFD codes based on Python (Dedalus, SpectralDNS) and
% Fortran (NS3D) are presented and qualitatively and quantitatively compared to
% \fluidpack{sim}.
% %
% The source code is hosted at Bitbucket as a Mercurial repository
% \href{https://bitbucket.org/fluiddyn/fluidsim}{bitbucket.org/fluiddyn/fluidsim}
% and the documentation generated using Sphinx can be read online at
% \href{https://fluidsim.readthedocs.io}{fluidsim.readthedocs.io}.
%
% \subsection{Keywords}
%
% % Python;\ CFD;\ HPC;\ MPI;\ modular;\ object-oriented;\ tested;\ documented;\
% % open-source
% 0D; 1D; 2D; 3D; pseudo-spectral; finite difference; computational fluid
% dynamics; sequential; MPI; GPU

\subsection{Introduction}

@@

\subsubsection{Performance}

@@

\subsection{pseudo-spectral code comparisons}

@@

\subsection{Quality control}

@@

\section{Availability}
\vspace{0.5cm}
\subsection{Operating system}

@@

\subsection{Programming language}

@@

\subsection{Dependencies}

@@

\subsection{List of contributors}

@@

\subsection{Software location}

\paragraph{\bf Archive}

@@

\subsection{Language}

@@

\section{Reuse potential}

@@

\subsection*{Acknowledgements}

@@

\subsection*{Funding statement}

@@

\subsection*{Competing interests}

@@

% \subsection{References}

@@

% \rule{\textwidth}{1pt}
\vspace{10pt}
\hrule
\vspace{10pt}

\paragraphbf{Copyright Notice}

Authors who publish with this journal agree to the following terms: \\
